Holomorphic field theories and higher algebra

### 2024-10-05 draft.tex
small additions

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \owen{is there some other place to point?} for more discussion.

@@

Given an invariant polynomial $\theta \in \Sym^{d+1}(\lie{g}^*)^G$ as in \S \ref{s:alghigh} we can obtain a twisted version of this $d$-polydisks algebra $A^{\lie{g}}_{d,\theta}$.
At the level of the punctured disk this corresponds to the higher Kac--Moody algebra that is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.

@@

\begin{rmk}
We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do. A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in \cite{Matsuoka}.~\hfill $\Diamond$
\end{rmk}

>>>>

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CLbcov, CLtypeI}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \owen{is there some other place to point?} for more discussion.

@@

Given an invariant polynomial $\theta \in \Sym^{d+1}(\lie{g}^*)^G$ as in \S \ref{s:alghigh} we can obtain a twisted version of this $d$-polydisks algebra $A^{\lie{g}}_{d,\theta}$.
At the level of the punctured disk this corresponds to the higher Kac--Moody algebra that is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra~\cite{GWonKM}.

@@

\begin{rmk}
We remark that Lurie and Ayala-Francis uses a different gluing axiom than we do. A careful comparison of the different axioms and a proof of their equivalence (for locally constant factorization algebras) can be found in~\cite{KSW}.~\hfill $\Diamond$
\end{rmk}
